\titleName{}

### 2015-12-07 FinalProject/Tex/paper/paper.tex
added abstract

\begin{abstract}
TODO This is my abstract. It has many pretty lorem ipsum words. Lorem ipsum
dolor sit amet, consectetur adipiscing elit. Aliquam nec est at nibh tempus
malesuada. Proin eget risus ut arcu imperdiet porttitor nec maximus est. Ut
vulputate gravida arcu vitae molestie. Vivamus tempor semper erat in
condimentum. Vestibulum tincidunt pulvinar dolor, sit amet tincidunt sem
sollicitudin et. Donec ut ultricies nulla, fringilla gravida neque. Sed feugiat
mauris eu enim ultricies, id tincidunt velit semper. Curabitur blandit diam
odio, in mollis risus porttitor eget. Vivamus rutrum enim turpis, eu posuere
nibh mattis porttitor. Aenean mollis augue nec semper porta. Nulla semper vitae
sapien quis commodo. Mauris tempor libero sollicitudin cursus lacinia.
\end{abstract}

>>>>

\begin{abstract}
This article is a survey of the current state of general-purpose computing on
GPUs (GPGPUs) and the use of heterogeneous applications on them. The underlying
architecture of GPUs is well-suited to problems with a high level of data
parallelism and has traditionally been used for rendering computer graphics.
Performing general-purpose computing on GPUs is a relatively recent development,
having only become practical and popular in the past decade or so. A brief
overview of a typical GPU architecture is presented, and the challenges of
applying this architecture to heterogeneous problems is discussed. Several
different current areas of research are explored, including warp compression,
dynamic tuning of warps, managing contention between CPUs and GPUs, and compiler
management of heterogeneous applications. While the challenges presented are
difficult to overcome, general-purpose computing on GPUs continues to make
progress in the areas of performance, energy, and power.
\end{abstract}
